Capitalized Title Here

### 2020-10-16 CMPSpaper_writing/CMPSpaper_writing.Rmd
updated the paper structure

Introduce the CMPS method/algorithm

* make it clear that we implemented the algorithm, not created it
* discuss a little that our data preparation method is different from that in the NIST paper. Shiny?

@@

How did we implement the algorithm

* how to present this? examples
* how detailed?

@@

* apply it to Hamby252 -> able to reproduce results in NIST paper qualitatively
* (?) apply it to Hamby44, using Hamby252 (default) parameters
* apply it to Hamby44, using parameters such that `lengths` represents the same actual length (the same amount of pixels of the scan)

@@

@@

* (?) potential flaws of the implementation
* Suggestion of how to select parameters
* open source implementation:
  - allow everyone to use, introduce the algorithm to R community
  - in general, open source implementation could reduce the level of ambiguity

>>>>

Address the problem: examiner - the two pattern evidence come from the same source or not

criticism of subjective methodology (report, citation) - why we need algorithms

Introduce our methodology - with 3D scans, digital microscope, data and algorithms

hambyset as the dataset

A short example to illustrate how one can use this CMPS package to obtain a comparison

* 2 lands - the same source; 1 land from another; signatures; CMPS score;

briefly talk about the CMPS method/algorithm, provide details in the Implementation section

* make it clear that we implemented the algorithm, not created it

outline what is going to come

@@

discuss a little that our data preparation method is different from that in the NIST paper. Shiny?

* [how do we get the signatures? ]

description of the algorithm and how did we implement it?

how would people use it?

@@

* apply it to Hamby252 -> able to reproduce results in NIST paper qualitatively
  - exclude some (?) scans because they are bad -> go further in Conclustion
  - [CHECK] Did researchers exclude those scans in NIST paper?
* apply it to another dataset, which have a different resolution
  - potential issues -> go further in Conclusion
  - need to use a different set of parameters
* apply it to Hamby44, what did we do?
  - using parameters such that `lengths` represents the same actual length (the same amount of pixels of the scan)

@@

(Our opinions)

@@

* (?) potential flaws of the implementation
* potential issues related to the algorithm
  - 6 as a cutoff?
    - not crossvalidated
    - estimate KM KNM distribution, etc...
  - choose parameters
* Suggestion of how to select parameters
* what should we do about higher resolution data? what did we do? [CHECK: what did NIST paper do]
* excluding outliers ? [check NIST paper]
* open source implementation:
  - allow everyone to use, introduce the algorithm to R community
  - in general, open source implementation could reduce the level of ambiguity
